Appendix S3. Hypotheses and tests for increased importance of evolutionary drivers for species and community dynamics

### 2024-10-01 manuscript/Appendix_S3_v01.Rmd
added sim, arranged folders, began metacom scenario

---
title: "Appendix S2. Evolutionary drivers of species and community dynamics"
author:
  - Jelena H. Pantel^[Laboratoire Chrono-environnement,UMR 6249 CNRS-UFC, 16 Route de Gray, 25030 Besançon cedex, France, jelena.pantel@univ-fcomte.fr]
  - Ruben J. Hermann^[University of Duisburg-Essen, Universitätsstraße 5, 45141 Essen, Germany, ruben.hermann@uni-due.de]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
    fig_caption: yes
    latex_engine: xelatex
    extra_dependencies: ["float"]
  bookdown::html_document2: default
  word_document:
    reference_docx: docx_template.docx
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[L]{Author Pantel and Hermann}
- \fancyhead[R]{Detection of ecoevo dynamics}
- \usepackage{lineno}
- \linenumbers
link-citations: yes
linkcolor: blue
csl: the-american-naturalist.csl
bibliography: refs.bib
---

@@

In Appendix S1.5, we evaluated the ability of the statistical model to estimate the impact of trait evolution for species abundances. Trait evolution's impact for species abundances can be modeled as a predictor in different ways. Here we derive the numerical form of the trait $x_i$ that we hypothesize has the most impact on species abundances.

>>>>

---
title: "Appendix S3. Hypotheses and tests for increased importance of evolutionary drivers for species and community dynamics"
author:
  - Jelena H. Pantel^[Laboratoire Chrono-environnement,UMR 6249 CNRS-UFC, 16 Route de Gray, 25030 Besançon cedex, France, jelena.pantel@univ-fcomte.fr]
  - Ruben J. Hermann^[University of Duisburg-Essen, Universitätsstraße 5, 45141 Essen, Germany, ruben.hermann@uni-due.de]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
    fig_caption: yes
    latex_engine: xelatex
    extra_dependencies: ["float"]
  bookdown::html_document2: default
  word_document:
    reference_docx: docx_template.docx
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[L]{Author Pantel and Hermann}
- \fancyhead[R]{Detection of ecoevo dynamics}
- \usepackage{lineno}
- \linenumbers
link-citations: yes
linkcolor: blue
csl: the-american-naturalist.csl
bibliography: refs.bib
---

@@

First I establish a metacommunity simulation scenario where environment, spatial random effects, and year-based Random Effects (species interactions) all play a role in driving species abundances. I then add in trait evolution, and look at its relative importance.
